A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-22 paper/fascd.tex
address PEF comments; see a few ELB comments remaining

{\color{blue} ELB: beam 2d example?}

@@

To allow box constraints on all meshes in the hierarchy, let $\tilde{\mathcal{V}}^j$ denote the set of functions on the vertices of $\mathcal{T}^j$ with values in the extended real line $\tilde{\RR} = [-\infty,+\infty]$.  The finest-level \emph{lower} and \emph{upper obstacles} $\underline{\gamma}^J, \overline{\gamma}^J \in \tilde{\mathcal{V}}^J$ are constructed by suitable interpolation of $\underline{\gamma}$, $\overline{\gamma}$ (e.g.~by applying the Cl\'ement interpolation operator) and satisfy
\begin{equation}
\underline{\gamma}^J \le \overline{\gamma}^J, \qquad \underline{\gamma}^J < +\infty, \qquad -\infty < \overline{\gamma}^J. \label{eq:fe:boxconstraintrequirements}
\end{equation}
Analogously, we construct the discrete boundary data $g_D^J$ so that $\underline{\gamma}^J \le g_D^J \le \overline{\gamma}^J$ on those vertices of $\mathcal{T}^J$ which lie in $\partial_D \Omega$.  Define
\begin{equation}
\mathcal{K}^J = \left\{w\,:\,\underline{\gamma}^J \le w \le \overline{\gamma}^J \text{ on vertices of } \mathcal{T}^J, \, \text{ and } \, w|_{\partial_D\Omega} = g_D^J|_{\partial_D\Omega}\right\} \subset \mathcal{V}^J, \label{eq:fe:fineconstraintset}
\end{equation}
the finest-level \emph{constraint set} of admissible FE functions. This is a nonempty, closed, and convex subset of $\mathcal{V}^J$.

@@

Canonical prolongation $P:\mathcal{V}^{j-1}\to\mathcal{V}^j$ implements the vector space inclusion $\mathcal{V}^{j-1} \hookrightarrow \mathcal{V}^j$ of coarser-mesh functions.  Canonical (dual) restriction $R:(\mathcal{V}^j)'\to(\mathcal{V}^{j-1})'$ also acts as an identity in the sense that if $\sigma \in (\mathcal{V}^j)'$ then $(R\sigma)[z] = \sigma[z]$ for all $z \in \mathcal{V}^{j-1} \subset \mathcal{V}^j$.  These canonical transfers generally involve a change of FE representation.  For example, $R$ is ``full-weighting'' \cite{Trottenbergetal2001}.

To define injection $\iR:\mathcal{V}^j\to\mathcal{V}^{j-1}$, observe that the vertices of $\mathcal{T}^{j-1}$ are vertices of $\mathcal{T}^j$, and that for any values at $\mathcal{T}^j$ vertices there is a unique $\mathcal{V}^j$ function assuming those values.  For $z\in\mathcal{V}^j$ we define the injection $\iR z$ as the element of $\mathcal{V}^{j-1}$ with the same (coarse) nodal values.  Injection is monotonic: if $w \le z$ then $\iR w \le \iR z$.

The monotone injections $\maxR,\minR$ \cite{GraeserKornhuber2009}, which will only be applied to nodal functions $\tilde{\mathcal{V}}^j$, are nonlinear maps which maximize and minimize, respectively, nodal values over the open supports of coarser-mesh basis functions (i.e.~over the \emph{stars} of the coarse vertices), Figure \ref{fig:Rplusminus}. These operators are constructed to enforce the property
\begin{equation}
\minR z \le z \le \maxR z,  \label{eq:fe:monotonerestrictionprops}
\end{equation}
which does not hold for the standard injection operator $\iR$.
To make the construction precise, let $x_q^j$ denote the vertices of mesh $\mathcal{T}^j$, with corresponding basis functions $\psi_q^j(x)$.  For a $\tilde\RR$-valued nodal function $z\in\tilde{\mathcal{V}}^j$ we define functions in $\tilde{\mathcal{V}}^{j-1}$:
\begin{align}
(\maxR z)(x_p^{j-1}) &= \max \{z(x_q^j) \,:\, \psi_p^{j-1}(x_q^j) > 0\}, \label{eq:fe:monotonerestrictions} \\
(\minR z)(x_p^{j-1}) &= \min \{z(x_q^j) \,:\, \psi_p^{j-1}(x_q^j) > 0\}. \notag
\end{align}
For standard refinement a coarse-mesh node $x_p^{j-1}$ is in the set of fine vertices $x_q^j$ such that $\psi_p^{j-1}(x_q^j)>0$, so \eqref{eq:fe:monotonerestrictionprops} follows.
On the other hand, $z\ge 0$ implies $\minR z \ge 0$ and $z \le 0$ implies $\maxR z \le 0$.  These ordering properties are used in the CD construction of the next two Sections.
\pef{Promote this to its own numbered equation and highlight its importance later on in the construction of LDCs}

@@

\begin{example}  \label{ex:directRbad}  
Let $\Omega = (0,L) \subset \RR^1$ and consider a two-level mesh hierarchy ($J=1$).  Let $\underline{\gamma}^1$ be a sawtooth function with minimum value zero, and suppose $\overline{\gamma}^1=C+\underline{\gamma}^1$ with $C>0$ strictly less than the maximum of $\underline{\gamma}^1$.  Figure \ref{fig:directRbad} shows such functions; here levels $\mathcal{T}^1$ and $\mathcal{T}^0$ have $5$ and $3$ vertices, respectively.  Ignoring the boundary for simplicity, the fine-level constraint set $\mathcal{K}^1$ defined by \eqref{eq:fe:fineconstraintset} is nonempty.  However, various natural schemes to coarsen the constraints, applied directly to $\underline{\gamma}^1,\overline{\gamma}^1$, are problematic.  Suppose we propose
\begin{equation}
    \label{eq:fe:standardinjection}
    \underline{\gamma}^0, \overline{\gamma}^0 \equiv \iR \underline{\gamma}^1, \iR \overline{\gamma}^1. \qquad \text{\emph{[problematic]}}
\end{equation}
Then $\underline{\gamma}^0=0$ and $\overline{\gamma}^0=C$ identically.  In that case the corresponding constraint set $\mathcal{K}^0$ is nonempty, but prolongation $Pw^0$ of an admissible solution of the coarse problem ($\underline{\gamma}^0 \le w^0 \le \overline{\gamma}^0$) is not admissible on the finer level: $Pw^0 \notin \mathcal{K}^1$.  On the other hand, suppose we propose
\begin{equation}
    \label{eq:fe:monotoneinjection}
    \underline{\gamma}^0, \overline{\gamma}^0 \equiv \maxR \underline{\gamma}^1, \minR \overline{\gamma}^1. \qquad \text{\emph{[problematic]}}
\end{equation}
The general motivation for this choice---compare \eqref{eq:fe:chilevels} below---is that $w^0 \ge \underline{\gamma}^0 \, \implies \, Pw^0 \ge \underline{\gamma}^1$ and $w^0 \le \overline{\gamma}^0 \, \implies \, Pw^0 \le \overline{\gamma}^1$.  However, in this case the coarse-level set $\mathcal{K}^0$ is empty because the proposed lower bound $\underline{\gamma}^0$ exceeds the proposed upper bound $\overline{\gamma}^0$ (Figure \ref{fig:directRbad}).
\end{example}

@@

Descending coarser levels, $j=J-1,\dots,1,0$, we next apply the monotone injections to generate \emph{level defect constraints} (LDCs) in $\tilde{\mathcal{V}}^j$:
\begin{equation}
\underline{\chi}^{j} = \maxR \underline{\chi}^{j+1}, \qquad \overline{\chi}^{j} = \minR \overline{\chi}^{j+1}. \label{eq:fe:chilevels}
\end{equation}
Observe that
\begin{equation}
\underline{\chi}^{J} \le \dots \le \underline{\chi}^0 \le 0 \le \overline{\chi}^0 \le \dots \le \overline{\chi}^J. \label{eq:fe:chiordering}
\end{equation}
A unilateral $J=4$ example of LDCs $\underline{\chi}^j$ is shown in Figure \ref{fig:chiphilevels}.  The LDC $\underline{\chi}^j$ is the most-negative function from $\tilde{\mathcal{V}}^j$ such that if another element of $\tilde{\mathcal{V}}^j$ is above $\underline{\chi}^j$ then it is also above $\underline{\chi}^{j+1}$; similar comments apply to $\overline{\chi}^{j}$.  Note that for Algorithm \ref{alg:fascd} below, any system satisfying \eqref{eq:fe:chiordering} will suffice; the particular formulas in \eqref{eq:fe:chilevels} are not required.

@@

In unilateral cases we can also construct decomposition operators $\Pi_i$ and thereby show property \eqref{eq:constraintrestrictionsum}.  For concreteness suppose $\overline{\gamma}^J=+\infty$, thus $\overline{\chi}^j=+\infty$ and $\overline{\phi}^i = +\infty$ for all levels.  For $v\in \mathcal{V}^j$ and $0\le i \le j$, let $I_{j\to i}^\ominus$ be the operator applying the minimum (monotone) injection $j-i$ times, mapping into $\mathcal{V}^i$:
\begin{equation}
I_{j\to i}^\ominus v = \minR(\dots(\minR v)\dots)  \label{eq:fe:minimummaps}
\end{equation}
(Set $I_{j\to j}^\ominus v = v$ and $I_{j\to -1}^\ominus=0$ by definition.)  Now define the following nonlinear decomposition operators $\Pi_i:\mathcal{U}^j \to \mathcal{D}^i$:
\begin{equation}
\Pi_i z^j = I_{j\to i}^\ominus(z^j - \underline{\chi}^j) - I_{j\to i-1}^\ominus(z^j - \underline{\chi}^j) + \underline{\phi}^i.  \label{eq:fe:unilateraldecompositionoperator}
\end{equation}
(Compare equation (4.9) in \cite{GraeserKornhuber2009}.)  Property \eqref{eq:fe:monotonerestrictionprops} implies $I_{j\to i}^\ominus(z^j - \underline{\chi}^j) \ge I_{j\to i-1}^\ominus(z^j - \underline{\chi}^j)$, thus $\Pi_i z^j \ge \underline{\phi}^i$, so $\Pi_i z^j \in \mathcal{D}^i$.  On the other hand, the following sum telescopes, leaving only its first term plus the sum in \eqref{eq:fe:telescoping}:
\begin{align*}
\sum_{i=0}^j \Pi_i z^j &= z^j - \underline{\chi}^j + \sum_{i=0}^j \underline{\phi}^i = z^j.
\end{align*}
This shows \eqref{eq:constraintrestrictionsum}, thus that \eqref{eq:fe:downwardsuminclusion} is equality, yielding \eqref{eq:constraintdecomp}.  The $\underline{\gamma}^J=-\infty$ case is similar.
\end{proof}

@@

This F-cycle approach is described in Algorithm \ref{alg:fascd-fcycle}.  In contrast to the construction of LDCs (Section \ref{sec:cdmultilevel}) for V-cycles, standard injection is used to generate the $\underline{\gamma}^j,\overline{\gamma}^j$ on each level during the initial nested iteration. This is because nested iteration approximates the full solution on the coarse grids, not just a correction to an initial iterate; essentially, our choice is between \eqref{eq:fe:standardinjection} (where the coarse constraint set is always nonempty, but the solution may not be admissible on the next level) or \eqref{eq:fe:monotoneinjection} (where the coarse solution is always admissible if it exists, but the constraint set may be empty). We choose \eqref{eq:fe:standardinjection} so that the coarse problems always have nonempty constraint sets, and project pointwise to the bounds as we refine in the nested iteration.
On line \ref{line:fcyclecoarsestinitial}, one may generate an initial iterate $w^0\in\mathcal{K}^0$ by injection and truncation of a finest-level iterate, if one is available.

@@

@@

%While an an extension to nonlocal, non-differential VI problems is of interest, it was not tried here

\subsection*{Code availability} \label{sec:code}  For reproducibility we have archived the exact software versions used to produce the results in this paper, including the correct Firedrake version, at {\color{blue} ELB: Zenodo?}

@@

The downward $\mathcal{D}^j$ and upward $\mathcal{U}^j$ constraint sets are also enlarged to vector spaces, and the corrections $y^j$ and $z^j$ are unconstrained; lines \ref{line:vcyclegenchifinest}, \ref{line:vcyclegenchi}, and \ref{line:vcyclegenphi} in Algorithm \ref{alg:fascd} can be removed.  In fact, VI problems \eqref{eq:fe:downvi} and \eqref{eq:fe:upvi} can be rewritten as the weak form problem $\ip{f^j(u^j)}{v} = \ip{\ell^j}{v}$ over $v\in \mathcal{V}_0^j$---this groups $u^j=w^j+y^j$ when down-smoothing and $u^j=w^j+z^j$ when up-smoothing---and the smoothers can be regarded as unconstrained, in-place modifications of $u^j$.  Noting line \ref{line:vcyclerestrictsolution} now says $u^{j-1}=\iR u^j$, after down-smoothing the coarsened source functional computed by line \ref{line:vcyclerestrictell} can be rewritten as $\ell^{j-1} = f^{j-1}\left(u^{j-1}\right) + R\left(\ell^j-f^j(u^j)\right)$.

@@

With these modifications, Algorithm \ref{alg:fascd} becomes the FAS V-cycle below, as a solver for \eqref{eq:app:fas:pde}.  This algorithm appears in various sources in the literature, for example \cite[Algorithm 14]{Bruneetal2015} and \cite[section 5.3.4]{Trottenbergetal2001}.

>>>>

\elb{beam 2d example?}

@@

To construct box constraints on all meshes in the hierarchy, let $\tilde{\mathcal{V}}^j$ denote the set of functions on the vertices of $\mathcal{T}^j$ with values in the extended real line $\tilde{\RR} = [-\infty,+\infty]$.  The finest-level \emph{lower} and \emph{upper obstacles} $\underline{\gamma}^J, \overline{\gamma}^J \in \tilde{\mathcal{V}}^J$ are constructed by suitable interpolation of $\underline{\gamma}$, $\overline{\gamma}$ (e.g.~by applying the Cl\'ement interpolation operator \elb{cite?}).  They must satisfy
\begin{equation}
\underline{\gamma}^J \le \overline{\gamma}^J, \qquad \underline{\gamma}^J < +\infty, \qquad -\infty < \overline{\gamma}^J. \label{eq:fe:boxconstraintrequirements}
\end{equation}
Analogously, we construct the discrete boundary data $g_D^J$ so that $\underline{\gamma}^J \le g_D^J \le \overline{\gamma}^J$ on those vertices of $\mathcal{T}^J$ which lie in $\partial_D \Omega$.  Then we define
\begin{equation}
\mathcal{K}^J = \left\{w\,:\,\underline{\gamma}^J \le w \le \overline{\gamma}^J \text{ on vertices of } \mathcal{T}^J, \, \text{ and } \, w|_{\partial_D\Omega} = g_D^J|_{\partial_D\Omega}\right\} \subset \mathcal{V}^J, \label{eq:fe:fineconstraintset}
\end{equation}
the finest-level \emph{constraint set} of admissible FE functions. This is a nonempty, closed, and convex subset of $\mathcal{V}^J$.

@@

Canonical prolongation $P:\mathcal{V}^{j-1}\to\mathcal{V}^j$ implements the vector space inclusion $\mathcal{V}^{j-1} \hookrightarrow \mathcal{V}^j$ of coarser-mesh functions.  Canonical (dual) restriction $R:(\mathcal{V}^j)'\to(\mathcal{V}^{j-1})'$ also acts as an identity in the sense that if $\sigma \in (\mathcal{V}^j)'$ then $(R\sigma)[z] = \sigma[z]$ for all $z \in \mathcal{V}^{j-1} \subset \mathcal{V}^j$.  These canonical transfers generally involve a change of FE representation; $R$ is ``full-weighting'' \cite{Trottenbergetal2001}.

To define injection $\iR:\mathcal{V}^j\to\mathcal{V}^{j-1}$, note that the vertices of $\mathcal{T}^{j-1}$ are vertices of $\mathcal{T}^j$.  For $z\in\mathcal{V}^j$ we define $\iR z$ as the element of $\mathcal{V}^{j-1}$ with the same (coarse) nodal values.  Injection is monotonic: if $w \le z$ then $\iR w \le \iR z$.

The monotone injections $\maxR,\minR$ \cite{GraeserKornhuber2009}, which will only be applied to constraints in $\tilde{\mathcal{V}}^j$, are nonlinear maps which maximize and minimize, respectively, nodal values over the open supports of coarser-mesh basis functions (i.e.~over the stars of the coarse vertices), Figure \ref{fig:Rplusminus}. These operators are constructed to enforce the property
\begin{equation}
\minR z \le z \le \maxR z,  \label{eq:fe:monotoneproperty}
\end{equation}
which does not hold for the standard injection operator $\iR$.
To make the construction precise, let $x_q^j$ denote the vertices of mesh $\mathcal{T}^j$, with corresponding basis functions $\psi_q^j(x)$.  For a $\tilde\RR$-valued nodal function $z\in\tilde{\mathcal{V}}^j$ we define functions in $\tilde{\mathcal{V}}^{j-1}$:
\begin{align}
(\maxR z)(x_p^{j-1}) &= \max \{z(x_q^j) \,:\, \psi_p^{j-1}(x_q^j) > 0\}, \label{eq:fe:monotoneinjections} \\
(\minR z)(x_p^{j-1}) &= \min \{z(x_q^j) \,:\, \psi_p^{j-1}(x_q^j) > 0\}. \notag
\end{align}
For standard refinement a coarse-mesh node $x_p^{j-1}$ is in the set of fine vertices $x_q^j$ such that $\psi_p^{j-1}(x_q^j)>0$, so \eqref{eq:fe:monotoneproperty} follows.  In the next Section we use $\maxR,\minR$ to construct ``level defect constraints'' such that the zero function is always admissible.  This construction depends on an additional ordering property of the monotone injections:
\begin{equation}
z\ge 0 \implies \minR z \ge 0, \qquad z \le 0 \implies \maxR z \le 0. \label{eq:fe:monotoneadditional}
\end{equation}

@@

\begin{example}  \label{ex:directRbad}  
Let $\Omega = (0,L) \subset \RR^1$ and consider a two-level mesh hierarchy ($J=1$).  Let $\underline{\gamma}^1$ be a sawtooth function with minimum value zero, and suppose $\overline{\gamma}^1=C+\underline{\gamma}^1$ with $C>0$ strictly less than the maximum of $\underline{\gamma}^1$.  Figure \ref{fig:directRbad} shows such functions; here levels $\mathcal{T}^1$ and $\mathcal{T}^0$ have $5$ and $3$ vertices, respectively.  Ignoring the boundary for simplicity, the fine-level constraint set $\mathcal{K}^1$ defined by \eqref{eq:fe:fineconstraintset} is nonempty.  However, various natural schemes to coarsen the constraints, applied directly to $\underline{\gamma}^1,\overline{\gamma}^1$, are problematic.  Suppose we propose
\begin{equation}
    \label{eq:fe:badstandard}
    \underline{\gamma}^0, \overline{\gamma}^0 \equiv \iR \underline{\gamma}^1, \iR \overline{\gamma}^1. \qquad \text{\emph{[problematic]}}
\end{equation}
Then $\underline{\gamma}^0=0$ and $\overline{\gamma}^0=C$ identically.  In that case the corresponding constraint set $\mathcal{K}^0$ is nonempty, but prolongation $Pw^0$ of an admissible solution of the coarse problem ($\underline{\gamma}^0 \le w^0 \le \overline{\gamma}^0$) is not admissible on the finer level: $Pw^0 \notin \mathcal{K}^1$.  On the other hand, suppose we propose
\begin{equation}
    \label{eq:fe:badmonotone}
    \underline{\gamma}^0, \overline{\gamma}^0 \equiv \maxR \underline{\gamma}^1, \minR \overline{\gamma}^1. \qquad \text{\emph{[problematic]}}
\end{equation}
The general motivation for this choice---compare \eqref{eq:fe:chilevels} below---is that $w^0 \ge \underline{\gamma}^0 \, \implies \, Pw^0 \ge \underline{\gamma}^1$ and $w^0 \le \overline{\gamma}^0 \, \implies \, Pw^0 \le \overline{\gamma}^1$.  However, in this case the coarse-level set $\mathcal{K}^0$ is empty because the proposed lower bound $\underline{\gamma}^0$ exceeds the proposed upper bound $\overline{\gamma}^0$ (Figure \ref{fig:directRbad}).
\end{example}

@@

Descending coarser levels, $j=J-1,\dots,1,0$, we next apply the monotone injections to generate \emph{level defect constraints} (LDCs) in $\tilde{\mathcal{V}}^j$:
\begin{equation}
\underline{\chi}^{j} = \maxR \underline{\chi}^{j+1}, \qquad \overline{\chi}^{j} = \minR \overline{\chi}^{j+1}. \label{eq:fe:chilevels}
\end{equation}
Observe that by \eqref{eq:fe:monotoneproperty} and \eqref{eq:fe:monotoneadditional},
\begin{equation}
\underline{\chi}^{J} \le \dots \le \underline{\chi}^0 \le 0 \le \overline{\chi}^0 \le \dots \le \overline{\chi}^J. \label{eq:fe:chiordering}
\end{equation}
A unilateral $J=4$ example of LDCs $\underline{\chi}^j$ is shown in Figure \ref{fig:chiphilevels}.  The LDC $\underline{\chi}^j$ is the most-negative function from $\tilde{\mathcal{V}}^j$ such that if another element of $\tilde{\mathcal{V}}^j$ is above $\underline{\chi}^j$ then it is also above $\underline{\chi}^{j+1}$; similar comments apply to $\overline{\chi}^{j}$.  Note that for Algorithm \ref{alg:fascd} below, any system satisfying \eqref{eq:fe:chiordering} will suffice; the particular formulas in \eqref{eq:fe:chilevels} are not required.

@@

In unilateral cases we can also construct decomposition operators $\Pi_i$ and thereby show property \eqref{eq:constraintrestrictionsum}.  For concreteness suppose $\overline{\gamma}^J=+\infty$, thus $\overline{\chi}^j=+\infty$ and $\overline{\phi}^i = +\infty$ for all levels.  For $v\in \mathcal{V}^j$ and $0\le i \le j$, let $I_{j\to i}^\ominus$ be the operator applying the minimum (monotone) injection $j-i$ times, mapping into $\mathcal{V}^i$:
\begin{equation}
I_{j\to i}^\ominus v = \minR(\dots(\minR v)\dots)  \label{eq:fe:minimummaps}
\end{equation}
(Set $I_{j\to j}^\ominus v = v$ and $I_{j\to -1}^\ominus=0$ by definition.)  Now define the following nonlinear decomposition operators $\Pi_i:\mathcal{U}^j \to \mathcal{D}^i$:
\begin{equation}
\Pi_i z^j = I_{j\to i}^\ominus(z^j - \underline{\chi}^j) - I_{j\to i-1}^\ominus(z^j - \underline{\chi}^j) + \underline{\phi}^i.  \label{eq:fe:unilateraldecompositionoperator}
\end{equation}
(Compare equation (4.9) in \cite{GraeserKornhuber2009}.)  Property \eqref{eq:fe:monotoneproperty} implies $I_{j\to i}^\ominus(z^j - \underline{\chi}^j) \ge I_{j\to i-1}^\ominus(z^j - \underline{\chi}^j)$, thus $\Pi_i z^j \ge \underline{\phi}^i$, so $\Pi_i z^j \in \mathcal{D}^i$.  On the other hand, the following sum telescopes, leaving only its first term plus the sum in \eqref{eq:fe:telescoping}:
\begin{align*}
\sum_{i=0}^j \Pi_i z^j &= z^j - \underline{\chi}^j + \sum_{i=0}^j \underline{\phi}^i = z^j.
\end{align*}
This shows \eqref{eq:constraintrestrictionsum}, thus that \eqref{eq:fe:downwardsuminclusion} is equality, yielding \eqref{eq:constraintdecomp}.  The $\underline{\gamma}^J=-\infty$ case is similar.
\end{proof}

@@

This F-cycle approach is described in Algorithm \ref{alg:fascd-fcycle}.  In contrast to the construction of LDCs (Section \ref{sec:cdmultilevel}) for V-cycles, standard injection is used to generate the $\underline{\gamma}^j,\overline{\gamma}^j$ on each level during the initial nested iteration. This is because nested iteration approximates the full solution on the coarse grids, not just a correction to an initial iterate; essentially, our choice is between \eqref{eq:fe:badstandard} (where the coarse constraint set is always nonempty, but the solution may not be admissible on the next level) or \eqref{eq:fe:badmonotone} (where the coarse solution is always admissible if it exists, but the constraint set may be empty). We choose \eqref{eq:fe:badstandard} so that the coarse problems always have nonempty constraint sets, and project pointwise to the bounds as we refine in the nested iteration.
On line \ref{line:fcyclecoarsestinitial}, one may generate an initial iterate $w^0\in\mathcal{K}^0$ by injection and truncation of a finest-level iterate, if one is available.

@@

\elb{beam example?}

@@

\subsection*{Code availability} \label{sec:code}  The software used to produce the results is archived at tag \elb{FIX} in the repository \url{https://bitbucket.org/pefarrell/fascd/}, using the Firedrake version \elb{what version?}

@@

The downward $\mathcal{D}^j$ and upward $\mathcal{U}^j$ constraint sets are also enlarged to vector spaces, and the corrections $y^j$ and $z^j$ are unconstrained; lines \ref{line:vcyclegenchifinest}, \ref{line:vcyclegenchi}, and \ref{line:vcyclegenphi} in Algorithm \ref{alg:fascd} can be removed.  Then VI problems \eqref{eq:fe:downvi} and \eqref{eq:fe:upvi} can be rewritten as the weak form problem $\ip{f^j(u^j)}{v} = \ip{\ell^j}{v}$ over $v\in \mathcal{V}_0^j$, where $u^j=w^j+y^j$ when down-smoothing and $u^j=w^j+z^j$ when up-smoothing, and the smoothers can be regarded as unconstrained, in-place modifications of $u^j$.  Noting line \ref{line:vcyclerestrictsolution} now says $u^{j-1}=\iR u^j$, after down-smoothing the coarsened source functional computed by line \ref{line:vcyclerestrictell} can be rewritten as $\ell^{j-1} = f^{j-1}\left(u^{j-1}\right) + R\left(\ell^j-f^j(u^j)\right)$.

@@

With these modifications, Algorithm \ref{alg:fascd} becomes the FAS V-cycle below, as a solver for \eqref{eq:app:fas:pde}.  It appears in various literature, for example \cite[Algorithm 14]{Bruneetal2015} and \cite[section 5.3.4]{Trottenbergetal2001}.
